BurgerTown Presents: Open Adcess

### 2017-04-23 digital-library.tex
current
?

\section{Digital Library}
\label{sec:lib}
Shady websites have long managed to monetize free content downloads.
Below we detail the ways in which we can follow their example to provide free
access to papers.

@@

The free tier will only allow downloads at slow speeds and no more than one
paper per day.
Additionally, the user will be required to stare at a screen compelling them to
upgrade while a counter decrements for 10 minutes before the download button is
clickable.
If the website loses focus, the counter will be restarted.
The \premium tier will allow unlimited downloads and will not be rate limited.

@@

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the users desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM Digital Library toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

@@

In order to comply with New Jersey's backwards laws about involuntary Bitcoin
mining \cite{tidbit}, all New Jersey residents will be preemptively banned from
the ACM Digital Library.

>>>>

\section{Digital Library}
\label{sec:lib}
Shady websites have long managed to monetize free content downloads.
Below we detail the ways in which we can follow their example to provide free
access to papers and liberate the ACM reader from covetousness.

@@

The free tier will only allow downloads at slow speeds and no more than one
paper per day.
Additionally, the user will be required to stare at a screen compelling them to
upgrade while a counter decrements for 10 minutes before the download button is
clickable.
If the engagement of the user---monitored via gaze tracker and wearable heart-rate monitor---falls below the zone of synergy, the counter will be restarted.
The \premium tier will allow unlimited downloads and will not be rate limited.

@@

\subsection{ACM Digital Library Toolbar}
Every ACM paper will be distributed as an executable.
Running this executable will ``install" the paper to the user's desktop.
The only purpose of the install is to push the ACM Digital Library toolbar on
the user.
While the toolbar itself is optional, its installation is opt-out.
The ACM Digital Library toolbar will be installed for the user's web browsers where it
will follow them from site to site collecting information about their browsing
habits.
We will then sell this information to advertisers.

@@

In order to comply with New Jersey's backwards laws about involuntary Bitcoin
mining \cite{tidbit}, all New Jersey residents will be preemptively banned from
the ACM Digital Library and the greater academic community.
